### 2020-04-06 paper/spor.tex
Revises the security analysis of SPOR

\((d, \pk_d, a_d)\gets \GetNode\): The algorithm~\(\GetNode\) returns a tuple 
\((d, \pk_d, a_d)\) of one selected node, where
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(a_d\gets \avail(d)\) is the availability of device~\(d\), where the 
    function~\(\avail\colon \devices\to \interval{0}{1}\) maps a device to its 
    availability (0 is always offline, 1 is always online).
\end{itemize}
We note that the function~\(\avail\) does note necessarily have to return the 
exact availability of \(d\), \eg it can provide \(k\)-anonymity by mapping the 
\(d\)'s availability to the closest of some predefined availability values, 
such as \(\{0.25, 0.5, 0.75, 1\}\).

@@

When Bob runs \(\CreateReply\) he must supply a set of nodes for each layer of 
the route, \(L = \{L_0, \dotsc, L_\nu\}\), where \(|L_i| \leq w_L\) for \(0\leq 
i\leq \nu\).
The set \(L_\nu\) contains only one or more of Bob's devices.
For the other layers, \(L_i\) for \(i < \nu\), Bob will do the following:
Bob makes \((\nu-1)\cdot w_L\) queries to \(\GetNode\) to get enough nodes to 
fill all remaining layers.
Bob will distribute these nodes across all layers~\(L_i\) to maximize the 
availability~\[
  a_{L_i} = 1 - \prod_{d\in L_i} (1-a_d)
\] of every layer (or equivalently, minimizing the risk that every node in a 
layer is offline at the same time).

>>>>

\((d, \pk_d, a_d)\gets \GetNode\): We assume that there exists an 
algorithm~\(\GetNode\) which returns a tuple \((d, \pk_d, a_d)\) of one 
selected node, where
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(a_d\gets \avail(d)\) is the availability of device~\(d\), where the 
    function~\(\avail\colon \devices\to \interval{0}{1}\) maps a device to its 
    availability (0 is always offline, 1 is always online).
\end{itemize}
We note that the function~\(\avail\) does note necessarily have to return the 
exact availability of \(d\), \eg it can provide \(k\)-anonymity by mapping the 
\(d\)'s availability to the closest of some predefined availability values, 
such as \(\{0.25, 0.5, 0.75, 1\}\).

@@

Now we can construct the layers of Bob's reply block that Alice can use to send 
him a message.
We provide the algorithm \(\CreateLayers\), which populates the layers~\(L_0, 
\dotsc, L_{\nu-1}\) that Bob must provide to \(\CreateReply\).
(Bob will create \(L_\nu\) himself by filling it with his devices.)

\((L_0, \dotsc, L_{\nu-1}) \gets \CreateLayers\):
The algorithm first makes \(\nu\cdot w_L\) queries to \(\GetNode\) to get 
enough nodes to fill all layers.
These nodes are distributed across all layers~\(L_i\), for \(0\leq i < \nu\), 
to maximize the availability~\[
  a_{L_i} = 1 - \prod_{d\in L_i} (1-a_d)
\] of every layer (or equivalently, minimizing the risk that every node in a 
layer is offline at the same time) while keeping \(|L_i| = w_L\).
